---
title: "Exercise 5"
output: html_notebook
---

Time: 2 1/2 hours

Loading all of the appropriate libraries:

```{r}
library(tidyverse)
library(dplyr)
library(purrr)
```

Importing the data (took a few tries because typos):

```{r}
names <- read_csv("namestib.csv")
```

Making sure everything imported correctly:

```{r}
names
```

Presenting .csv data in a tibble so as to manipulate it with ggplot (also made some other small modifications to the .csv file for ease of use)

```{r}
namestib <- as_tibble(names)
```

Attempting to do some kind of preliminary plotting with ggplot (not 100% sure what my goals are here which is all-around not best practice):

```{r}
ggplot(data = namestib) +
  geom_point(mapping = aes(x= Name, y = Source))
```

This particular plot is not very helpful. None of the names can be read. What if I switch the axes?

```{r}
ggplot(data = namestib) +
  geom_point(mapping = aes(x = Source, y = Name))
```

Still not very decipherable, and I've left a whole column unaccounted for. Maybe we can work with size and color?

```{r}
ggplot(data = namestib) +
 geom_point(mapping = aes(x = Source, y = Name, color = Role))
```

While they're not rendering in the Markdown notebook well, they render better in the console. Either way, this is still not the best way to present the information. I want to emphasize the people who appeared in more than one source. Maybe if I try to switch the variable around?

```{r}
ggplot(data = namestib) +
 geom_point(mapping = aes(x = Role, y = Name, color = Source))
```

Still not getting my point across, but this is the best way to present the information I've come across so far. Let's try to use size--that wil make it clearer where I hope the viewer will look.

```{r}
ggplot(data = namestib) +
  geom_point(mapping = aes(x = Role, y = Name, size = Source))
```

Here R helpfully pointed out that that's not exactly how size should be used. Off to do more research.

I didn't exactly get to where I was going but I maintain that the graph which sorted the roles by color is okay. I got frustrated here but didn't want to read ahead to try to find the answers I wanted as I still wasn't confident I was doing the assignment correctly (was I supposed to use Open Refine?), so I decided to stop. I think one of the reasons I'm finding this so difficult is because there aren't any numbers in my data but I'm trying to plot it numerically. It's especially aggravating because I know what I want the plot to look like and I know the number counts that I need but I am struggling to make it work in R.
